### 2014-02-17 classicthesis/RelatedWork.tex
distributed stochastic gradient descent

\section{Low complexity learning}

@@

>>>>

\section{Low complexity Learning-to-Rank}

@@

\section{Distributed Stochastic Gradient Descent}
Long et al\cite{Long2012} describe special case of their pairwise cross-domain factor Learning-to-Rank method using distributed optimization of \ac{SGD} based on Hadoop MapReduce. Parallelisation of the \ac{SGD} optimization algorithm was performed using the MapReduce based method described by  Zinkevich et al\cite{Zinkevich2010} has been used. Real world data from Yahoo! has been used to show that the model is effective. Unfortunately the speed-up obtained by training their model in parallel is not reported.
